Truthfulness Verification System

### 2011-05-04 proposal/paper.tex
example for alg 1 added

\subsection{Bag of words}

\begin{algorithm}
\small
\caption{Ranking Algorithm 1}
\label{alg:AssignScore1} 
\begin{algorithmic}
\STATE \textbf{Description}: Given the alternate units generated by the current T-verifier system, rank the units in descending order of truthfulness using Wikipedia
\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each line in this file is a tuple containing the sentence id, the alternate units generated and the topic unit.
\STATE \textbf{Output}: Ranked alter\_units 
\FOR {each sentence $s_{i}$}
	\STATE $tu_{i}$ = topic unit string
	\STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)

	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
	\ENDFOR
	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
	\ENDFOR	
	%\FOR{every wiki\_article $w_{p}$ in $list_wiki_articles_au_{s_{i}}$ }
	%	$bow_w_{p}$ = generate\_bag\_of\_words($w_{p}$)	
	%	\FOR {every wiki\_article $w_{j}$ in $list_wiki_articles_tu_{j}$  }	
	%	\ENDFOR
	%\ENDFOR
\ENDFOR

@@

\begin{enumerate}
\item Step I: Detection of wiki articles from $DU$, $AU$, $TU$.
\begin {enumerate}
\item For the $AU$s, we take the words as they appear in the output of T-verifier(mainly because most of them are single word). For $TU$ we use a basic exponential algorithm that takes all possible combinations of the content words.
\item The default configuration of T-verifier generates a total of 5 $AU$s, without any ranking.  For each content word in a $AU$, or a combination of words in case the $AU$ consists of multiple content words, we check if there exists a wikipedia article. There may be three cases:
\begin{enumerate}
\item No article. Continue with next word or word combination. 
\item One article. Go to next step
\item More than one article. The page lands into a "disambiguation" page. We discuss this later. 
\end{enumerate}
\end{enumerate}
\item We remove the html tags from the pages, and convert them into simple bag of words. Repetation of a word if any is retained.
\item We select the following pairwise combination - a wikiarticle detected from $AU$, ($W_{au_{i}}$) and a wikiarticle detected from $TU$ ($W_{tu_{j}}$).
\item We take the common words $c_{ij} = {w_{1}, w_{2}, \ldots}$ matched by regular expressions in these two bags.
\item Since this is a regular expression matching we will have two different values for $c_{ij}$ = common($W_{au_{i}}$, $W_{tu_{j}}$) and $c_{ji}$ = common($W_{tu_{j}}$, $W_{au_{i}}$). This is explained below.
\item In this collection of common words, $c_{ij}$, we search each of the content words of the $TU$, not included in the title of $W_{tu_{j}}$ 
\item We observe the maximum number of matches in all of such interesctions and use the count to rank the $AU$-s generated by T-verifer. 
\end{enumerate}

\paragraph{Handling Disambiguation}
For the testing that we have done with the five problematic sentences, we manually first used the disambiguation page itself in the above process. But as expected, it did not yeild good results. We are experimenting with the following ideas for disabmigutation.
\begin{enumerate}
\item Apply the above steps for each of the page linked from the disambiguation page and get the one which gives the maximum count
\item Use the heading under which it appears in the disambiguation page, the one sentence summary appearing adjacent to the entry in the disambiguation page, and the "Categories" under which a particular article has been tagged.
\end{enumerate}
For this report, we manually checked the disambiguation pages by searching them for content words. This significantly improved the results.

\paragraph{Word matching}
We found that the intersection of the two bags of words, $W_{au_{i}}$ and $W_{tu_{i}}$ produced different results based on the ordereing of the articles while performing the intersection operation. This is because the regular expression match finds the maximal match. Lets consider that the first file, $W_{au_{i}}$ has "invent", and the second file, $W_{tu_{i}}$ has "invented", and "inventor". So when we pick a word in $W_{au_{i}}$ and try to match words in $W_{tu_{i}}$, we will find 2 matches. However, the words from second file, both "invented", and "inventor" will not find any matches in ($W_{au_{i}}$). Taking both way intersections will ensure we do not miss out different morphological variations of the same word appearing in the context common to the both articles.

\paragraph{Example}

A description of the above steps applied to the five problematic sentences
\begin{enumerate}
\item Sentence 1: Les Paul invented the electric guitar.
\begin{enumerate}
\item AU: Les\_Paul, Gibson Les, Leo, Llyod, Adolph Rickenbacker. 
\item Wiki articles detected from AU($W_{au_{i}}$): Les\_Paul, Leo (disambiguation page), Adolph\_Rickenbacker 
\item Wiki articles detected from TU($W_{tu_{i}}$): The\_guitar, The\_Electric\_guitar, Electric\_guitar, invented Invention 
\end{enumerate}

\item Sentence 2: Tom Hanks is the lead actress of the movie Sleepless in Sattle.
\begin{enumerate}
\item AU: hanks meg, meg ryan, tom hanks, nora, sam
\item Wiki articles detected from AU($W_{au_{i}}$): Meg\_Ryan, Tom\_Hanks, Nora(Disambiguation), Sam(Disambiguation page) 
\item Wiki articles detected from TU($W_{tu_{i}}$): Sleepless\_in\_Seattle, Lead, Lead-in, Leading\_actor(automatically redirected from Leading actress), Movie(automatically redirected from Film), Sleepless(disambiguation page), Seattle(lands on the correct page, though there is a disambiguation page).
\end{enumerate}

\item Sentence 3: Apollo was the first spacecraft on the moon.
\begin{enumerate}
\item AU: apollo, land, landing, luna
\item Wiki articles detected from AU($W_{au_{i}}$): Apollo, Land(disambiguation page), Landing(disambiguation page), Luna(disambiguation)
\item Wiki articles detected from TU($W_{tu_{i}}$): Fisrt(disambiguation page), Moon, Spacecraft.
\end{enumerate}

\item Sentence 4: english is the primary language of the philippines.
\begin{enumerate}
\item AU: english, filipino, spansih, education, history
\item Wiki articles detected from AU($W_{au_{i}}$): English disambiguation page), Filipino(disambiguation page), Spanish(disambiguation), Education, History
\item Wiki articles detected from TU($W_{tu_{i}}$): Primary (disambiguation page), language(disambiguation page), First\_Language (automatically redirected from Primary Languge), Philippines.

\end{enumerate}

\item Sentence 5: Michael Phelps is the fastest swimmer in the world
\begin{enumerate}
\item AU: michael, long, ernest, sullivan, alexander
\item Wiki articles detected from AU($W_{au_{i}}$): Michael, Alexander, Sullivan(disambiguation page), Long(disambiguation page), Ernest(disambiguation page) 
\item Wiki articles detected from TU($W_{tu_{i}}$): Fastest, Swimming(sport) (automatically redirected from Swimmer),World.

\end{enumerate}

\end{enumerate}

Please refer to the hand out analysis of the results.

@@

\paragraph{Examples}
Examples of the algorithm described above is discussed below. The algorithm 2 produce perfect result for three of the five sentences. But it struggles with the remaining two sentences. However, the algorithm 2 primarily augment the algorithm 1 and add strength to the results from algorithm 1. Hence they work better together and produce overall better output.

\paragraph{Tom Hanks was the lead actress  int move 'Sleepless in Seattle'}
The alternative units for this sentence are "Tom Hanks", "Meg Ryan", "Hanks Meg", "Nora", and "Sam". Here the sentence containing "Tom Hanks" contain the word actor but not actress. So the algorithm classify it as false. But the sentence containing "Meg Ryan" has the word actress and hence classify it as true. For other alternative units, we don't even get any sentences containing the alternative unit. So the algorithm produce an unambiguous single true statement for this sentence.

\paragraph{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.

\paragraph{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.

\paragraph{English is the Primary Language of the Philippines}
The alternative units for this sentence are "English", "Filipino", "Spanish", "Education", and "History". Our current algorithm struggle with this sentence because of occurrence of content words and alternative units in the same sentence for all the alternative units. So it classify all of them as true and assign same weight to all of them. However, as our algorithm 1 can rank the alternative units in correct order, merged rank from algorithm 1 and algorithm 2 is still correct and produce overall correct result.

\paragraph{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.

\subsection{Rank merging}
This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.

>>>>

\subsection{Bag of words}
In the bag of words method, we are exploiting the fact that for true sentence we will have high content word match between pages obtained from topic unit and alternate units. Overall steps of this method are described below:
\begin{itemize}
\item For all possible k-grams $(k=1,2,3,...,topic\_unit\_length)$ of topic unit we find relevant wikipedia page using wikipedia search API. Although it may seems that taking all possible k-grams will introduce noise in the retrieved data, this is not the case because there will be no pages for irrelevant k-gram consisting of irrelevant combination of words. Now for each possible k-gram we may get a Wikipedia page directly or we may go need to disambiguate if that k-gram refers to multiple possible pages in Wikipedia. If we get a single page without any ambiguation then we take that page. However, if we need to disambiguate then we look into all possible wikipedia pages and disambiguate them using highest intersection of words of topic unit and description of the wikipedia page for the disambiguation link. Here we take all words except the k-gram for which we are disambiguating as a set of words for intersection. So assume that at the end of this step we get $n$ wikipedia pages either directly or through disambiguation.

\item Now for each of the five alternative units generated by the T-verifier we also find a wikipedia page. Here also we may get a Wikipedia page directly or we may need to disambiguate if there are multiple possible pages. If we need disambiguation then we disambiguate using same approach described previously i.e. maximal intersection of words between the description of disambiguation link and words of topic unit.

\item We have five Wikipedia pages for each of the alternative units now and $n$ pages from topic unit. We generate bag of words i.e. content words for all the five pages for alternate units and $n$ pages for topic unit.

\item Now for each of the page corresponding to alternate units we count intersection of words for each $n$ pages for topic unit and take sum of  intersection count for an alternate unit page and $n$ topic unit page. Hence at this step we have a count value associated with each of the alternate unit and we rank all the alternate units according to this value to produce truth confidence or rank for all five alternate units.
\end{itemize}

Pseudo-code for Bag of words ranking is given below. Listing \ref{alg:BagOfWords} produces the ranking for all five alternative units following the procedure described above. It uses Listing \ref{alg:findwikiarticles} to generate k-grams and find relevant Wikipedia pages and Listing \ref{alg:disambiguate} to disambiguate among alternative pages using intersection of words between topic unit and description of disambiguation link for alternative page

%\begin{algorithm}
%\small
%\caption{Bag of Words (Algorithm 1)}
%\label{alg:AssignScore1} 
%\begin{algorithmic}
%\STATE \textbf{Description}: Given the alternate units generated by the current T-verifier system, rank the units in descending order of truthfulness using Wikipedia
%\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each line in this file is a tuple containing the sentence id, the alternate units generated and the topic unit.
%\STATE \textbf{Output}: Ranked alter\_units 
%\FOR {each sentence $s_{i}$}
%	\STATE $tu_{i}$ = topic unit string
%	\STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)
%		
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR
%	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
%		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
%	\ENDFOR	
%	%\FOR{every wiki\_article $w_{p}$ in $list_wiki_articles_au_{s_{i}}$ }
%	%	$bow_w_{p}$ = generate\_bag\_of\_words($w_{p}$)	
%	%	\FOR {every wiki\_article $w_{j}$ in $list_wiki_articles_tu_{j}$  }	
%	%	\ENDFOR
%	%\ENDFOR
%\ENDFOR
%
%
%\end{algorithmic}
%\end{algorithm}
%

\begin{algorithm}
\small
\caption{Bag of Words (Ranking Algorithm 1)}
\label{alg:BagOfWords}
\begin{algorithmic}
\STATE \textbf{Description}: Given the alternate units generated by
the current T-verifier system, rank the units in descending order of
truthfulness using Wikipedia
\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each
line in this file is a tuple containing the sentence id, the alternate
units generated and the topic unit.
\STATE \textbf{Output}: Ranked alter\_units
\FOR {each sentence $s_{i}$}
       \STATE $tu_{s_{i}}$ = topic unit string
       \STATE $s_{i}.au\_list$ = alternate units generated by T-verifier
       \STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)

       \FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
               \STATE $w_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
               \IF {$w_{s_{i}.au_{j}}$ == $\phi$}
                       \STATE skip to processing next $w_{s_{i}.au_{j}}$
               \ENDIF
               \IF {$w_{s_{i}.au_{j}}$ is diambiguation page}
                       \STATE $w_{s_{i}.au_{j}}$ = disambiguate($w_{s_{i}.au_{j}}$)
                       \STATE $bow_{s_{i}.au_{j}}$ = generate\_bag\_of\_words($s_{i}.au_{j}$)
               \ENDIF
       \ENDFOR
       \FOR {each $w_{s_{i}.tu_{j}}$ in $s_{i}.tu\_list$ }
               \STATE $bow_{s_{i}.tu_{j}}$ = generate\_bag\_of\_words($s_{i}.tu_{j}$)
       \ENDFOR

       \FOR {$s_{i}.au_{j}$ in $s_{i}.au\_list$}
               \FOR {each $w_{s_{i}.tu_{k}}$ in $s_{i}.tu\_list$ }
                       \STATE $ common\_words^{au_{j}}_{tu_{k}} $ =  $bow_{s_{i}.au_{j}}
\cap bow_{s_{i}.tu_{k}}$
                       \STATE $ remaining\_words_{s_{i}.tu_{k}}$  = $ tu_{s_{i}}$ - words
forming title of $w_{s_{i}.tu_{j}} $ - stop words
                       \FOR {each word $w$ in $ remaining\_words_{s_{i}.tu_{k}}$}
                               \STATE $s_{i}.au_{j}.score$ += count of $w$
                       \ENDFOR
               \ENDFOR
       \ENDFOR
\STATE print $s_{i}.au_{j}$ reverse sorted by $s_{i}.au_{j}.score$
\ENDFOR

@@

\pagebreak

\begin{algorithm}
\small
\caption{Find wiki articles (called from Bag of Words)}
\label{alg:findwikiarticles}
\begin{algorithmic}
\STATE \textbf{Description}: Given a string of words determine phrases
that may be titles of wikipedia articles
\STATE \textbf{Input}: a string of words $s$
\STATE $l$ = length($s$)
\STATE $result$ = $\phi$
\FOR{$i$ in 1 to $l$}
       \FOR{$j$ in $i$ to $l$}
               \STATE $sub\_string_{ij}$ += $s_i$ + $blank$
       \ENDFOR
       \IF{ $sub\_string_{ij}$ consits only stopwords}
               \STATE discard and continue to next interation
       \ELSE
               \STATE search wikipedia with $sub_string_{ij}$
               \STATE $result_{sub\_string_{ij}}$ = (displaytitle, url, categories,
redirects) for $sub\_string_{ij}$
       \ENDIF
\ENDFOR
\RETURN result
\end{algorithmic}
\end{algorithm}

\pagebreak

\begin{algorithm}
\small
\caption{Disambiguate articles (called from Bag of Words)}
\label{alg:disambiguate}
\begin{algorithmic}
\STATE \textbf{Description}: Given a disambiguation page returns the
wikipedia article that is most relevant to setence being processed
\STATE \textbf{Input}: disambiguation page $p$,$tu_{s_{i}}$
\STATE extract all outlinks urls from the body of the page
\STATE form a dictionary $d$ using disambiguation element ($de$) and
the disambiguation description ($dd$) appearing adjacent to the $de$
\FOR {every $de$ in $d$}
       \STATE $de.ddscore$ = count content word overlap between $dd$ and
($tu_{s_{i}}$ - words in  $de$)
\ENDFOR
%\STATE form a dictionary $l$ using disambiguation element ($de$) and
%the lead section ($ls$) appearing as the first paragraph of the
%article in $de$
%\FOR {every $de$ in $l$}
%       \STATE $de.lsscore$ = count content word overlap between $ls$ and
%($tu_{s_{i}}$ - words in  $de$)
%\ENDFOR
%\STATE form a dictionary $c$ using disambiguation element ($de$) and
%the category list ($cl$) appearing attached with the article on $de$
%\FOR {every $de$ in $c$}
%       \FOR {every category in $cl$}
%               \STATE $de.clscore$ = count content word overlap between $cl$ and
%($tu_{s_{i}}$ - words in  $de$)
%       \ENDFOR
%\ENDFOR
%\STATE Reverse sort the $de$s in each method using the scores
%\STATE Use Bordas ranking or weighted Bordas to merge the ranks
\RETURN top ranked $de$
\end{algorithmic}
\end{algorithm}

%\begin{enumerate}
%\item Step I: Detection of wiki articles from $DU$, $AU$, $TU$.
%\begin {enumerate}
%\item For the $AU$s, we take the words as they appear in the output of T-verifier(mainly because most of them are single word). For $TU$ we use a basic exponential algorithm that takes all possible combinations of the content words.
%\item The default configuration of T-verifier generates a total of 5 $AU$s, without any ranking.  For each content word in a $AU$, or a combination of words in case the $AU$ consists of multiple content words, we check if there exists a wikipedia article. There may be three cases:
%\begin{enumerate}
%\item No article. Continue with next word or word combination. 
%\item One article. Go to next step
%\item More than one article. The page lands into a "disambiguation" page. We discuss this later. 
%\end{enumerate}
%\end{enumerate}
%\item We remove the html tags from the pages, and convert them into simple bag of words. Repetation of a word if any is retained.
%\item We select the following pairwise combination - a wikiarticle detected from $AU$, ($W_{au_{i}}$) and a wikiarticle detected from $TU$ ($W_{tu_{j}}$).
%\item We take the common words $c_{ij} = {w_{1}, w_{2}, \ldots}$ matched by regular expressions in these two bags.
%\item Since this is a regular expression matching we will have two different values for $c_{ij}$ = common($W_{au_{i}}$, $W_{tu_{j}}$) and $c_{ji}$ = common($W_{tu_{j}}$, $W_{au_{i}}$). This is explained below.
%\item In this collection of common words, $c_{ij}$, we search each of the content words of the $TU$, not included in the title of $W_{tu_{j}}$ 
%\item We observe the maximum number of matches in all of such interesctions and use the count to rank the $AU$-s generated by T-verifer. 
%\end{enumerate}
%
%
%\paragraph{Handling Disambiguation}
%For the testing that we have done with the five problematic sentences, we manually first used the disambiguation page itself in the above process. But as expected, it did not yeild good results. We are experimenting with the following ideas for disabmigutation.
%\begin{enumerate}
%\item Apply the above steps for each of the page linked from the disambiguation page and get the one which gives the maximum count
%\item Use the heading under which it appears in the disambiguation page, the one sentence summary appearing adjacent to the entry in the disambiguation page, and the "Categories" under which a particular article has been tagged.
%\end{enumerate}
%For this report, we manually checked the disambiguation pages by searching them for content words. This significantly improved the results.
%
%\paragraph{Word matching}
%We found that the intersection of the two bags of words, $W_{au_{i}}$ and $W_{tu_{i}}$ produced different results based on the ordereing of the articles while performing the intersection operation. This is because the regular expression match finds the maximal match. Lets consider that the first file, $W_{au_{i}}$ has "invent", and the second file, $W_{tu_{i}}$ has "invented", and "inventor". So when we pick a word in $W_{au_{i}}$ and try to match words in $W_{tu_{i}}$, we will find 2 matches. However, the words from second file, both "invented", and "inventor" will not find any matches in ($W_{au_{i}}$). Taking both way intersections will ensure we do not miss out different morphological variations of the same word appearing in the context common to the both articles.

\paragraph{Example}
Detail working of Bag of Words (Algorithm 1) for following sentence is given below:

\emph{Les Paul invented the electric guitar}

For this sentence, the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. At first, we generate all possible k-grams from the topic unit. The generated k-grams are following:

['invented', 'Invented', 'invented the', 'Invented The', 'invented the electric', 'Invented The Electric', 'invented the electric guitar', 'Invented The Electric Guitar', 'the', 'The', 'the electric', 'The Electric', 'the electric guitar', 'The Electric Guitar', 'electric', 'Electric', 'electric guitar', 'Electric Guitar', 'guitar', 'Guitar']

Now for each k-gram we find relevant wikipedia page. We will not get any wikipedia page for irrelevant k-gram combination.  Moreover, We may get a page directly or we may need to disambiguate. Following are the all relevant pages. The False in the second column page there is no ambiguation and True means we need to disambiguate.

\url{http://en.wikipedia.org/wiki/Invention}, False\\
\url{http://en.wikipedia.org/wiki/The_Electric}, True \\
\url{http://en.wikipedia.org/wiki/Electric_guitar}, False\\
\url{http://en.wikipedia.org/wiki/Electricity}, False \\
\url{http://en.wikipedia.org/wiki/Electric_guitar}, False \\
\url{http://en.wikipedia.org/wiki/Guitar}, False

For the above pages, we need to disambiguate for one page only and that is http://en.wikipedia.org/wiki/The\_Electric. We described earlier that we look into the count of overlap between topic unit words and disambiguation link description words. For this disambiguation there is no overlap and so we do not need to process this page further. Hence the final set of $n$ pages are following:

\url{http://en.wikipedia.org/wiki/Invention} \\
\url{http://en.wikipedia.org/wiki/Electric_guitar} \\
\url{http://en.wikipedia.org/wiki/Electricity} \\
\url{http://en.wikipedia.org/wiki/Electric_guitar} \\
\url{http://en.wikipedia.org/wiki/Guitar}

In the next step, we find relevant Wikipedia page for each of the alternate units. There are no relevant Wikipedia page for  gibson les and llyod. Hence we do not process these alternative units further. For the remaining three alternative units, there is no ambiguation for les paul and adolph rickenbacker. The corresponding pages are following:

\url{http://en.wikipedia.org/wiki/Les_Paul}\\
\url{http://en.wikipedia.org/wiki/Adolph_Rickenbacker}

However we need to disambiguate for the page corresponding to Leo:

\url{http://en.wikipedia.org/wiki/Leo}

After disambiguation for Leo using word overlap between description and topic unit words, we get following page:

\url{http://en.wikipedia.org/w/index.php?action=raw&title=Leo_(constellation)}

Now, we need to count word overlap for each of the pages for les paul, adolph rickenbacker, leo with all pages for the topic unit and take sum of the overlap to produce the ranking of alternate units

%A description of the above steps applied to the five problematic sentences
%\begin{enumerate}
%\item Sentence 1: Les Paul invented the electric guitar.
%\begin{enumerate}
%\item AU: Les\_Paul, Gibson Les, Leo, Llyod, Adolph Rickenbacker. 
%\item Wiki articles detected from AU($W_{au_{i}}$): Les\_Paul, Leo (disambiguation page), Adolph\_Rickenbacker 
%\item Wiki articles detected from TU($W_{tu_{i}}$): The\_guitar, The\_Electric\_guitar, Electric\_guitar, invented Invention 
%\end{enumerate}
%
%
%
%\item Sentence 2: Tom Hanks is the lead actress of the movie Sleepless in Sattle.
%\begin{enumerate}
%\item AU: hanks meg, meg ryan, tom hanks, nora, sam
%\item Wiki articles detected from AU($W_{au_{i}}$): Meg\_Ryan, Tom\_Hanks, Nora(Disambiguation), Sam(Disambiguation page) 
%\item Wiki articles detected from TU($W_{tu_{i}}$): Sleepless\_in\_Seattle, Lead, Lead-in, Leading\_actor(automatically redirected from Leading actress), Movie(automatically redirected from Film), Sleepless(disambiguation page), Seattle(lands on the correct page, though there is a disambiguation page).
%\end{enumerate}
%
%\item Sentence 3: Apollo was the first spacecraft on the moon.
%\begin{enumerate}
%\item AU: apollo, land, landing, luna
%\item Wiki articles detected from AU($W_{au_{i}}$): Apollo, Land(disambiguation page), Landing(disambiguation page), Luna(disambiguation)
%\item Wiki articles detected from TU($W_{tu_{i}}$): Fisrt(disambiguation page), Moon, Spacecraft.
%\end{enumerate}
%
%\item Sentence 4: english is the primary language of the philippines.
%\begin{enumerate}
%\item AU: english, filipino, spansih, education, history
%\item Wiki articles detected from AU($W_{au_{i}}$): English disambiguation page), Filipino(disambiguation page), Spanish(disambiguation), Education, History
%\item Wiki articles detected from TU($W_{tu_{i}}$): Primary (disambiguation page), language(disambiguation page), First\_Language (automatically redirected from Primary Languge), Philippines.
%
%\end{enumerate}
%
%
%\item Sentence 5: Michael Phelps is the fastest swimmer in the world
%\begin{enumerate}
%\item AU: michael, long, ernest, sullivan, alexander
%\item Wiki articles detected from AU($W_{au_{i}}$): Michael, Alexander, Sullivan(disambiguation page), Long(disambiguation page), Ernest(disambiguation page) 
%\item Wiki articles detected from TU($W_{tu_{i}}$): Fastest, Swimming(sport) (automatically redirected from Swimmer),World.
%
%\end{enumerate}
%
%
%\end{enumerate}
%
%Please refer to the hand out analysis of the results.

@@

\paragraph{Examples}
Detail working of Sentence Structure (Algorithm 2) for following sentence is given below:

\emph{Les Paul invented the electric guitar}

For this sentence the alternative units are les paul, gibson les, llyod, leo, adolph rickenbacker. The top wikipedia page from google search is \url{http://en.wikipedia.org/wiki/Electric_guitar}. So we download this page. Convert it to text from html and split into sentences. Then we match each alternate unit with all the sentences to see if there is any intersection with the alternate unit. We found intersection for the alternate units les paul, gibson les, llyod, and adolph rickenbaker but not for leo. Hence leo get a score of zero and we process other alternative units further. In the next step, we find intersection between content words or topic unit and matched sentences for alternate units found in the previous step. We count no of words that are overlapped and rank alternate units according to this count value. Count of the content word overlap is given below.

3 les paul\\
1 gibson les\\
0 llyod\\
0 leo\\
0 adolph rickenbacker

 It shows that we have 3 content word intersection for les paul, 1 word intersection for gibson les and 0 for all other alternate units. This ranking is the final truth or confidence ranking for all alternate units.

 %\paragraph{Examples}
%Examples of the algorithm described above is discussed below. The algorithm 2 produce perfect result for three of the five sentences. But it struggles with the remaining two sentences. However, the algorithm 2 primarily augment the algorithm 1 and add strength to the results from algorithm 1. Hence they work better together and produce overall better output.
%
%\paragraph{Tom Hanks was the lead actress  int move 'Sleepless in Seattle'}
%The alternative units for this sentence are "Tom Hanks", "Meg Ryan", "Hanks Meg", "Nora", and "Sam". Here the sentence containing "Tom Hanks" contain the word actor but not actress. So the algorithm classify it as false. But the sentence containing "Meg Ryan" has the word actress and hence classify it as true. For other alternative units, we don't even get any sentences containing the alternative unit. So the algorithm produce an unambiguous single true statement for this sentence.
%
%\paragraph{Les Paul invented the electric guitar}
%The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.
%
%\paragraph{Luna 2 is the first spacecraft on the moon}
%The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.
%
%\paragraph{English is the Primary Language of the Philippines}
%The alternative units for this sentence are "English", "Filipino", "Spanish", "Education", and "History". Our current algorithm struggle with this sentence because of occurrence of content words and alternative units in the same sentence for all the alternative units. So it classify all of them as true and assign same weight to all of them. However, as our algorithm 1 can rank the alternative units in correct order, merged rank from algorithm 1 and algorithm 2 is still correct and produce overall correct result. 
%
%\paragraph{Sullivan is the fastest swimmer in the world}
%The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.
%
%\subsection{Rank merging}
%This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.
%
%
